Open Split Tests

### 2021-06-10 inst/rmd/opensplittests.Rmd
Add section for new sample run.

```{r}
carb_data <- tribble(~vial, ~name, ~rec_num, ~mass,
                     1, "C-2_1", 1082, 6.03,
                     2, "C-2_2", 1082, 11.10,
                     3, "C-2_3", 1082, 15.52
                     )

@@

>>>>

```{r}
carb_data <- tribble(~, ~name, ~rec_num, ~mass,
                     1, "C-2_1", 1082, 6.03,
                     2, "C-2_2", 1082, 11.10,
                     3, "C-2_3", 1082, 15.52
                     )

@@

## 2021-06-11 Small(er) sample tests

Tested 8mg of C-1, C-2, and NOSAMS2 carbonate in vials backfilled with Helium.

```{r}
carb_data <- tribble(~name, ~rec_num, ~carbonate_mass, ~helium_added,
                     "C-1_1", 83028, 8.29,
                     "C-1_2", 83028, 9.01,
                     "C-1_3", 83028, 9.00,
                     "C-2_1", 1082, 8.23,
                     "C-2_2", 1082, 8.77,
                     "C-2_3", 1082, 7.34,
                     "NOSAMS-2_1", 38809, 7.72,
                     "NOSAMS-2_2", 38809, 7.69,
                     "NOSAMS-2_3", 38809, 8.86,
                     )

write_csv(carb_data, here("data/carb_data_2021-06-04.csv"))
insert_samples(carb_data)
carb_data
```

```{r}
df <- process_hgis_results(here("data/USAMS061121R.txt"), as.Date("2021-06-11")) #, standards)

insert_raw(df)
```

```{r}
df_sum <- sum_hgis_targets(df) %>% 
  norm_hgis() %>% 
  blank_cor_hgis()

insert_results(df_sum)
```
